%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Var Bhat's Resume in Latex                             %
% Author : Var Bhat                                      %
% Github : https://github.com/varbhat/resume             %
% Credits: https://github.com/sb2nov/resume              %
%          https://github.com/sc932/resume               %
% License : MIT License                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{article}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{hyperref}  
\usepackage{xcolor}

\input{glyphtounicode}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FONT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[sfdefault]{GoSans}
%\usepackage[default]{comicneue}
%\usepackage[sfdefault]{inter}
%\usepackage[sfdefault]{roboto}
%\usepackage[lf]{venturis}
%\usepackage[sfdefault]{noto}
%\usepackage[default]{lato}
%\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page Configuration and Styling %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}
%

\urlstyle{same}


\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\hypersetup{colorlinks,linkcolor={dark-blue},citecolor={dark-blue},urlcolor={dark-blue}}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Formatting of Sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF file is machine readable or parsable by ATC
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMMANDS %%%%%%%%%%%%%%%%%%%

\newcommand{\ResumeHeader}[6]{
\hspace*{\fill} {\scriptsize\color{gray}\emph{Last updated on \today}}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 #1 & #2 \\
 #3 & #4 \\
 #5 & #6 \\
\end{tabular*}
}

\newcommand{\EducationEntry}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\ProjectEntry}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand{\projectItemListStart}{\begin{itemize}[leftmargin=2mm]}
\newcommand{\projectItemListEnd}{\end{itemize}}
\newcommand{\projectItem}[1]{
  \item[$\diamond$]\small{
    {#1}
  }
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESUME %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%--------------HEADER-----------------------%
\ResumeHeader
{\textbf{\href{https://github.com/varbhat}{\Large\color{black}{Var Bhat}}}}   {\href{mailto:mailvarbhat@gmail.com}{mailvarbhat@gmail.com}}
{\href{https://github.com/varbhat}{github.com/varbhat}} {\href{https://linkedin.com/in/var-bhat}{linkedin.com/in/var-bhat}} 
{{Bangalore, India}}
{\href{tel:+919113612019}{+91 9113612019}}
%------------------------------------------%


%-----------EDUCATION----------------------%
\section{Education}
\resumeSubHeadingListStart
\EducationEntry
{Bachelor of Engineering in Computer Science}
{August 2019 -- (expected) June 2023}
{\href{https://vtu.ac.in}{Visvesvaraya Technological University}}
{Bangalore, India}
\resumeSubHeadingListEnd
\setlength{\columnsep}{0.5cm}
%-------------------------------------------%


%-----------PROJECTS-------------------------%
\setlength{\columnsep}{0.5cm}


%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/exatorrent}{Exatorrent}} $|$ \emph{Bittorrent Client written in Go}}{August 2021 -- Present}
\projectItemListStart
\projectItem{Developed Self-hostable , easy-to-use , lightweight and feature-rich torrent client written in Go . It comes with beautiful Web UI and Optional Multi-User Support . Run Locally or Host in Server . Open/Download/Stream Torrents in Browser Right Away! Thousands of Stars and 250k+ Pulls.}
\projectItem{Written in Go , Frontend in Typescript/Javascript and Svelte . Docker Image is provided. Automations using Github Actions (Earlier Prototypes in CircleCI , React , Vuejs ). Uses WebSockets and REST APIs. Provides WebHooks , Media Serving , System Monitoring (Prometheus). Sqlite3 and PostgreSQL are used as Database.}
\projectItemListEnd
\resumeSubHeadingListEnd
    
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/slocation}{Slocation}} $|$ \emph{Router in Javascript for Svelte}}{}
\projectItemListStart
\projectItem{Wrote Reactive Svelte Location Store which is Router for Svelte written in Javascript/Typescript. Published to NPM. Used in exatorrent.}
\projectItemListEnd
\resumeSubHeadingListEnd
    
    
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/bast}{bast}} $|$ \emph{Basic to C Transpiler}}{}
\projectItemListStart
\projectItem{Developed Transpiler which takes BASIC dialect Code as Input and transpiles it to C Program. Explored Textual Parsing and Generation.}
\projectItemListEnd
\resumeSubHeadingListEnd
    
    
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/void-container}{void-container}} $|$ \emph{Docker Images for Void Linux built weekly}}{}
\projectItemListStart
\projectItem{Void Linux CI/CD Docker Images are built weekly and on each push to the repository by Github Actions . Images are deployed in numerous Docker,Podman and Kubernetes Instances. Used Shell Scripting and Agile Methodologies.}
\projectItemListEnd
\resumeSubHeadingListEnd
    
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/crossmac}{crossmac}} $|$ \emph{Compile for MacOS in Linux}}{}
\projectItemListStart
\projectItem{Cross Compiler for MacOS available on Linux and Cloud.}
\projectItemListEnd
\resumeSubHeadingListEnd
    
 
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/serv}{serv}} $|$ \emph{File Directory Server}}{}
\projectItemListStart
\projectItem{Superfast HTTP Server to Serve Directories and SPAs. Log Requests on the go.}
\projectItemListEnd
\resumeSubHeadingListEnd


\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/remdl}{remdl}} $|$ \emph{Remote HTTP Downloader}}{}
\projectItemListStart
\projectItem{Self-Hostable Application to Remotely Download HTTP Files from Internet in Server. Concurrency and Scaling are explored.}
\projectItemListEnd
\resumeSubHeadingListEnd



    
    

    
    
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/varbhat/torpar}{torpar}} $|$ \emph{TUI Client to Search DHT Torrents}}{}
\projectItemListStart
\projectItem{Command Line TUI Application to Search Torrents in DHT.}
\projectItemListEnd
\resumeSubHeadingListEnd
    

\begin{center}
	\emph{\small Please refer to \href{https://github.com/varbhat}{Github Profile} for a more complete list of Projects.}
\end{center}
%----------------------------------------------%


%--------------- Technical Skills ---------------------%
\setlength{\columnsep}{1cm}
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeSubItem{Programming Languages}
{Go , Python , Javascript / Typescript , Java , Kotlin , C++ , Rust }
\resumeSubItem{Web Frameworks}
{React.js , Vue.js , Svelte , Next.js , Redux , Node.js , Express , Three.js}
\resumeSubItem{Backend}
{Chi , Gorilla , Node.js , Express , Flask , Django , FastAPI , Springboot , Ktor}
\resumeSubItem{Database}
{PostgreSQL , Sqlite3 , Redis , MongoDB , Cassandra , RocksDB , ElasticSearch}
\resumeSubItem{API}
{REST , WebSocket , GraphQL , gRPC}
\resumeSubItem{Cloud}
{AWS , GCP}
\resumeSubItem{Tools}
{Docker , Kubernetes , CI/CD , Jenkins , Git , Qemu/KVM , Nginx , Prometheus , Traefik , Nginx , Varnish }
\resumeSubItem{Other Frameworks}
{Tailwind CSS , Bootstrap CSS , MaterialUI , Jetpack , Jetpack Compose}
\resumeSubItem{Others}
{ Apache Kafka , RabbitMQ , Benthos , NATS , Celery}
\resumeSubItem{OS}
{Linux(Debian,Alpine) , FreeBSD , MacOS , Windows}
\resumeSubItem{Other Skills}
{Googling , Algorithms and Data Structures , Touch Typing , Self-Hosting , Designing and Administering Systems , \LaTeX}
\resumeSubItem{Languages}
{English\emph{(Full Professional Proficiency)}}
\resumeSubHeadingListEnd
%--------------------------------------------------------%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
